Efficient UQ for chemical systems using active \author{Manav Vohra, Alen Alexanderian, Hayley Guy, Sankaran Mahadevan} subspaces

### 2018-08-04 Paper/method.tex
..

\bigskip
\begin{breakablealgorithm}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
  \caption{An iterative gradient-based approach for discovering the active subspace}
  \begin{algorithmic}[1]
\Require $\theta_l$, $\theta_u$, $\tau$. 
\Ensure $\hat{\mat{\Lambda}}$, $\hat{\mat{W}}$, $\bm{\nu}_r(f)$ %$\eta$. %
    \Procedure{Gradient-based}{}
    \State Set $k$ = 0
	\State Draw $n_k$ random samples, $\{\bm{\xi}_i\}_{i=1}^{n_k}$ 
         according to $\pi$. 
    \State Set $N_\text{total}$ = $n_k$ 
	\iffalse \State Project to the physical space:
        $\{\bm{\theta}_k\}_{k=1}^{n_r}=\theta_l+0.5(\theta_u-\theta_l)\{\bm{\xi}_k\}_{k=1}^{n_r}$ \fi
	\State For each $i=1, \ldots, N_\text{total}$, compute $f(\bm{\xi}_i)$ and the gradient $\bm{g}^i = \nabla_{\bm{\xi}}f(\bm{\xi}_i)$
    \iffalse  
	\Statex\hspace{5mm} Using Finite Difference: 
	\Statex\hspace{5mm} i. Assign a small increment, $d\xi$.
	\Statex\hspace{5mm} ii. Augment the set of samples with neighboring points.
	\be \{\bm{\Xi}_k\}_{k=1}^{n_1(N_p+1)}:~\{\bm{\xi}_k\}_{k=1}^{n_1} \cup
        \{\xi_{k,j}+d\xi\}_{j=1}^{N_p} \nonumber
	\ee
	\Statex\hspace{5mm} iii. Project to the physical space:
        $\{\bm{\theta}_k\}_{k=1}^{n_1(N_p+1)}=\theta_l+0.5(\theta_u-\theta_l)\{\bm{\Xi}_k\}_{k=1}^{n_1(N_p+1)}$
	\Statex\hspace{5mm} iv. Using the augmented set, $\{\bm{\theta}_k\}_{k=1}^{n_1(N_p+1)}$
         compute $\bm{g}^i$.
         \fi 
	\State Compute $\hat{\mat{C}}$ and its eigenvalue decomposition 
		$\hat{\mat{C}}$= $\frac{1}{N_\text{total}}\sum\limits_{i=1}^{N_\text{total}}[\bm{g}^i][\bm{g}^i]^\top$ = 
		$\hat{\mat{W}}^{(k)}\hat{\mat{\Lambda}}^{(k)} \hat{\mat{W}}^{(k)\top}$
	%\State Eigenvalue decomposition, $\mat{C}$ = $W^{(0)}\Lambda^{(0)} W^{(0)\top}$%
	\State Partition: $\hat{\mat{\Lambda}}^{(k)}=
        \begin{bmatrix} \hat{\mat{\Lambda}}_1^{(k)} & \\ & \hat{\mat{\Lambda}}_2^{(k)} \end{bmatrix}$, 
        $\hat{\mat{W}}^{(k)}=\begin{bmatrix} \hat{\mat{W}}_1^{(k)} & \hat{\mat{W}}_2^{(k)} \end{bmatrix}$, 
        $\hat{\mat{\Lambda}}_1^{(k)}\in \mathbb{R}^{N_p\times r}$
	\Loop
		\State Set $k$ = $k$ + 1
		\State Draw $n_k =  \lceil\beta n_{k-1}\rceil$  new random samples 
                $\{\bm{\xi}_i\}_{i=1}^{n_k}$  $\beta\in[0,1]$  $k = n_{k-1}+1,\ldots,n_{k-1}+n_k$.

@@

In the gradient-free approach, the model output is first computed at an initial set of $n_1$ samples. An independent
set of $M$ samples is also drawn according to the joint probability distribution of the inputs. For each sample
in $M$, $p$ nearest neighbours in the $n_1$ set are identified. A least-squares fit to model evaluations at
the $p$ samples is performed. The slope vector ($\bm{b}_i$) of the regression-fit is stored separately and the process is
repeated for each sample in $M$. The symmetric and positive semi-definite matrix, $\hat{\mat{C}}$ is hence constructed
using the slope vectors as follows:
%
\be
\hat{\mat{C}} = \frac{1}{M}\sum\limits_{i=1}^{M}\bm{b}_i\bm{b}_i^\top = \hat{\bm{W}}\hat{\bm{\Lambda}}\hat{\bm{W}}^\top
\ee
%
Eigenvalue decomposition of $\hat{\mat{C}}$ yields an initial approximation to the
active subspace. The aforementioned sequence of steps is repeated until $\delta w_{1,j}^{(r)}$ as mentioned
earlier in~\ref{sub:grad} is found to be smaller than $\tau$. An outline of the gradient-free approach is
provided in Algorithm~\ref{alg:free1}, and the specific sequence of steps pertaining to the construction of
$\hat{\mat{C}}$ is provided in Algorithm~\ref{alg:free2}.

\bigskip
\begin{breakablealgorithm}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
  \caption{An iterative gradient-free approach for discovering the active subspace}
  \begin{algorithmic}[1]
\Require $\theta_l$, $\theta_u$, $M$, $\tau$. 
\Ensure $\Lambda$, $W$, $\alpha$ %$\eta$. 
    \Procedure{Gradient-free}{}
    \State Set $k$ = 0
	\State Draw $n_k$ random samples, $\{\bm{\xi}_j\}_{j=1}^{n_k}$
	\State Set $N_\text{total}$ = $n_k$ 
	\iffalse \State Project to the physical space:
        $\{\bm{\theta}_k\}_{i=1}^{n_k}=\theta_l+0.5(\theta_u-\theta_l)\{\bm{\xi}_k\}_{k=1}^{n_r}$
        \fi
     \State Draw $M$ random samples, $\{\bm{\nu}_i\}_{i=1}^{M}$ 
	\State Compute $f(\bm\xi_j)$, $j=1, \ldots, N_\text{total}$.
	\State Compute the matrix $\mathbb{C}$ and its eigenvalue decomposition using Algorithm 3
	%\State Eigenvalue decomposition, $\mat{C}$ = $W^{(r)}\Lambda^{(r)} W^{(r)\top}$
	\State Partition: $\Lambda^{(k)}~=~ 
        \begin{bmatrix} \Lambda_1^{(k)} & \\ & \Lambda_2^{(k)} \end{bmatrix}$, 
        $W^{(k)}~=~\begin{bmatrix} W_1^{(k)} & W_2^{(k)} \end{bmatrix}$, 
        $\Lambda_1^{(k)}\in \mathbb{R}^{d\times\mathcal{S}}$
	\Loop
		\State Set $k$ = $k$ + 1
		\State Draw $n_k =  \beta n_{k-1}$  new random samples 
		$\{\bm{\xi}_j\}_{j=1}^{n_k}$  $\beta =??$  $j = n_{k-1}+1,\ldots,n_{k-1}+n_k$. 
        \State $N_\text{total}$ = $N_\text{total}$ + $n_k$    
	\iffalse	\State Project $\bm{\xi}_k$~$\rightarrow$~$\bm{\theta}_k$. \fi

		\State Compute $f(\bm\xi_j)$, $j=n_{k-1}+1, \ldots, n_{k-1}+n_k$.  
		\State Construct the matrix, $\mat{C}$ and its eigenvalue decomposition
		\State Compute $\delta W_{1,j}^{(k)}$ = 
                       \scalebox{1.25}{$\frac{\|(W_{1,j}^{k})^2 - 
                       (W_{1,j}^{k-1})^2\|}{\|(W_{1,j}^{k-1})^2\|}$}, 
                       $j = 1,\ldots,\mathcal{S}$.
		\If {$\max\left(\delta W_{1,j}^{(k)}\right)<\tau$}
			\State break
		\EndIf
	\EndLoop
	\State Compute $\alpha_i(N_\text{total}) = \sum\limits_{j=1}^{\mathcal{S}} \Lambda_{1_{i,j}}W_{1_{i,j}}^2$,
	$i=1,\ldots,d$.
    \EndProcedure
  \end{algorithmic}
  \label{alg:free1}
\end{breakablealgorithm}
\bigskip

\bigskip
\begin{breakablealgorithm}
%\renewcommand{\algorithmicrequire}{\textbf{Input:}}
%\renewcommand{\algorithmicensure}{\textbf{Output:}}
  \caption{Algorithm for constructing the matrix, $\mat{C}$}
  \begin{algorithmic}[1]
	\Procedure{Local Linear Approximation}{} 
	\State Draw $N$ random samples, $\{\bm{\xi}_j\}_{j=1}^{N}$ 
	according to $\pi$.
	\iffalse \State Project to the physical space:
	$\{\bm{\theta}_k\}_{k=1}^{N}=\theta_l+0.5(\theta_u-\theta_l)\{\bm{\xi}_k\}_{k=1}^{N}$ \fi
	\State Compute $f(\bm\xi_j)$, $j=1, \ldots, N$.
	\State Draw $M$ random samples, $\{\bm{\nu}_i\}_{i=1}^{M}$
	according to $\pi$.
	\State Choose an integer $p \leq N$ 
	\State For each $i=1, \ldots, M$, compute 
	\[
	\begin{aligned}
	\Phi_i &= \{ p \text{ nearest points in } \{\bm{\xi}_j\}_{j=1}^{N} \text{ to } \bm{\nu}_i\}\\
	\vspace{-2mm}
	\Psi_i &= \text{subset of } f(\bm\xi_j) \text{ corresponding to the points in } \Phi_i
	\end{aligned}
	\]
	\State Compute linear least square fits 
	 $f(\bm\xi_j) \approx c_i + b_i^T\bm{\xi}_j$, \  $\bm{\xi}_j \in \Phi_i, \ f(\bm\xi_j) \in \Psi_i$
	\State Compute the matrix 
	\[
	\mat{C} \approx \frac{1}{M} \sum_{i=1}^{M} b_i b_i^T = {W}{\Lambda}{W}^T
	\]
	\EndProcedure
  \end{algorithmic}
  \label{alg:free2}
\end{breakablealgorithm}
\bigskip

@@

As mentioned earlier, the model output $f(\bm{\xi}(\bm{\theta}))$ predominantly varies in the active subspace. Hence, 
$f(\bm{\xi}(\bm{\theta}))$ can be transformed as a function of the active variable as $G(\bm{w}_1^\top\bm{\xi})$ in
the subspace. The plot of $G$ versus $\bm{w}_1^\top\bm{\xi}$, regarded as the \textit{sufficient summary plot} (SSP) is 
compared for the two approaches in Figure~\ref{fig:comp_ssp}.
%
\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.48\textwidth]{./Figures/comp_ssp}
\caption{An illustrative comparison of the SSPs generated using the gradient-based and the gradient-free approaches.}
\label{fig:comp_ssp}
\end{center}
\end{figure}
%
The two SSPs are observed to be in excellent agreement with each other. Moreover, it is interesting to note
that the variability in ignition
delay based on the considered prior marginals for $A_i$'s is observed to be approximately linear in the
active subspace; consistent with the fact the it is 1-dimensional.

We extend the comparative assessment of the two approaches by estimating the activity score for individual
uncertain parameters ($\alpha_i$) using
the components of the dominant eigenvector in the following equation:
%
\be
\alpha_i(n) = \sum\limits_{j=1}^{\mathcal{S}}\Lambda_{1_{i,j}}w_{1_{i,j}}^2,~i = 1,\ldots,N_p
\ee
%
where $n$ is the sample size. The activity scores for the 19 uncertain pre-exponents ($A_i$'s), estimated using
the two approaches are plotted in Figure~\ref{fig:comp_as} (left). Additionally, for the purpose of verification, we 
compare these estimates with those obtained using the DGSMs~\cite{Vohra:2018} in 
Figure~\ref{fig:comp_as} (right). 
%
\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.45\textwidth]{./Figures/comp_as}
  \includegraphics[width=0.45\textwidth]{./Figures/ub_conv_kinetics_rich}
\caption{Left: A bar-graph of activity scores ($\alpha_i$'s) for the 19 uncertain pre-exponents ($A_i$'s).
Right: A plot of the screening metric ($\widehat{\mathcal{C}_i\mu_i}$), defined as a normalized product of the
Poincare constant and the DGSM ($\mu_i$) (adapted from~\cite{Vohra:2018}).}
\label{fig:comp_as}
\end{center}
\end{figure}
%
The activity scores estimated using the two approaches agree favourably with each other as well as those
based on the screening metric involving the DGSMs from~\cite{Vohra:2018}. It is observed that the uncertainty
associated with the ignition delay is largely due to the uncertainty in $A_9$ and $A_1$. Sensitivity towards
$A_{15}$ and $A_{17}$ is also found to be significant.

>>>>

\bigskip
\begin{breakablealgorithm}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
  \caption{An iterative gradient-based approach for discovering the active subspace}
  \begin{algorithmic}[1]
\Require $\theta_l$, $\theta_u$, $\tau$. 
\Ensure $\hat{\mat{\Lambda}}$, $\hat{\mat{W}}$, $\bm{\nu}_r(f)$ %$\eta$. %
    \Procedure{Gradient-based}{}
    \State Set $k$ = 0
	\State Draw $n_k$ random samples, $\{\bm{\xi}_i\}_{i=1}^{n_k}$ 
         according to $\pi_{\bm{\xi}}$. 
    \State Set $N_\text{total}$ = $n_k$ 
	\iffalse \State Project to the physical space:
        $\{\bm{\theta}_k\}_{k=1}^{n_r}=\theta_l+0.5(\theta_u-\theta_l)\{\bm{\xi}_k\}_{k=1}^{n_r}$ \fi
	\State For each $i=1, \ldots, N_\text{total}$, compute $f(\bm{\xi}_i)$ and the gradient $\bm{g}^i = \nabla_{\bm{\xi}}f(\bm{\xi}_i)$
    \iffalse  
	\Statex\hspace{5mm} Using Finite Difference: 
	\Statex\hspace{5mm} i. Assign a small increment, $d\xi$.
	\Statex\hspace{5mm} ii. Augment the set of samples with neighboring points.
	\be \{\bm{\Xi}_k\}_{k=1}^{n_1(N_p+1)}:~\{\bm{\xi}_k\}_{k=1}^{n_1} \cup
        \{\xi_{k,j}+d\xi\}_{j=1}^{N_p} \nonumber
	\ee
	\Statex\hspace{5mm} iii. Project to the physical space:
        $\{\bm{\theta}_k\}_{k=1}^{n_1(N_p+1)}=\theta_l+0.5(\theta_u-\theta_l)\{\bm{\Xi}_k\}_{k=1}^{n_1(N_p+1)}$
	\Statex\hspace{5mm} iv. Using the augmented set, $\{\bm{\theta}_k\}_{k=1}^{n_1(N_p+1)}$
         compute $\bm{g}^i$.
         \fi 
	\State Compute $\hat{\mat{C}}$ and its eigenvalue decomposition 
		$\hat{\mat{C}}$= $\frac{1}{N_\text{total}}\sum\limits_{i=1}^{N_\text{total}}[\bm{g}^i][\bm{g}^i]^\top$ = 
		$\hat{\mat{W}}^{(k)}\hat{\mat{\Lambda}}^{(k)} \hat{\mat{W}}^{(k)\top}$
	%\State Eigenvalue decomposition, $\mat{C}$ = $W^{(0)}\Lambda^{(0)} W^{(0)\top}$%
	\State Partition: $\hat{\mat{\Lambda}}^{(k)}=
        \begin{bmatrix} \hat{\mat{\Lambda}}_1^{(k)} & \\ & \hat{\mat{\Lambda}}_2^{(k)} \end{bmatrix}$, 
        $\hat{\mat{W}}^{(k)}=\begin{bmatrix} \hat{\mat{W}}_1^{(k)} & \hat{\mat{W}}_2^{(k)} \end{bmatrix}$, 
        $\hat{\mat{\Lambda}}_1^{(k)}\in \mathbb{R}^{N_p\times r}$
	\Loop
		\State Set $k$ = $k$ + 1
		\State Draw $n_k =  \lceil\beta n_{k-1}\rceil$  new random samples 
                $\{\bm{\xi}_i\}_{i=1}^{n_k}$  $\beta\in[0,1]$  $k = n_{k-1}+1,\ldots,n_{k-1}+n_k$.

@@

In the gradient-free approach, the model output is first computed at an initial set of $n_1$ samples. An independent
set of $M$ samples is also drawn according to the joint probability distribution of the inputs. For each sample
in $M$, $p$ nearest neighbours in the $n_1$ set are identified. A least-squares fit to model evaluations at
the $p$ samples is performed. The slope vector ($\bm{b}_i$) of the regression-fit is stored separately and the process is
repeated for each sample in $M$. The symmetric and positive semi-definite matrix, $\hat{\mat{C}}$ is hence constructed
using the slope vectors as follows:
%
\be
\hat{\mat{C}} = \frac{1}{M}\sum\limits_{i=1}^{M}\bm{b}_i\bm{b}_i^\top = \hat{\bm{W}}\hat{\bm{\Lambda}}\hat{\bm{W}}^\top
\ee
%
Hence, the gradient-free approach essentially differs in the procedure for constructing the matrix, $\hat{\mat{C}}$.
The active subspace computation involves the same sequence of steps as outlined previously for the gradient-based 
approach in Algorithm~\ref{alg:grad}. The procedure for constructing $\hat{\mat{C}}$ using local linear approximation
of the model output is provided in Algorithm~\ref{alg:free2}.

%\bigskip
%\begin{breakablealgorithm}
%\renewcommand{\algorithmicrequire}{\textbf{Input:}}
%\renewcommand{\algorithmicensure}{\textbf{Output:}}
%  \caption{An iterative gradient-free approach for discovering the active subspace}
%  \begin{algorithmic}[1]
%\Require $\theta_l$, $\theta_u$, $M$, $\tau$. 
%\Ensure $\Lambda$, $W$, $\alpha$ %$\eta$. 
%    \Procedure{Gradient-free}{}
%    \State Set $k$ = 0
%	\State Draw $n_k$ random samples, $\{\bm{\xi}_j\}_{j=1}^{n_k}$
%	\State Set $N_\text{total}$ = $n_k$ 
%	\iffalse \State Project to the physical space:
%        $\{\bm{\theta}_k\}_{i=1}^{n_k}=\theta_l+0.5(\theta_u-\theta_l)\{\bm{\xi}_k\}_{k=1}^{n_r}$
%        \fi
%     \State Draw $M$ random samples, $\{\bm{\nu}_i\}_{i=1}^{M}$ 
%	\State Compute $f(\bm\xi_j)$, $j=1, \ldots, N_\text{total}$.
%	\State Compute the matrix $\mathbb{C}$ and its eigenvalue decomposition using Algorithm 3
%	%\State Eigenvalue decomposition, $\mat{C}$ = $W^{(r)}\Lambda^{(r)} W^{(r)\top}$
%	\State Partition: $\Lambda^{(k)}~=~ 
%        \begin{bmatrix} \Lambda_1^{(k)} & \\ & \Lambda_2^{(k)} \end{bmatrix}$, 
%        $W^{(k)}~=~\begin{bmatrix} W_1^{(k)} & W_2^{(k)} \end{bmatrix}$, 
%        $\Lambda_1^{(k)}\in \mathbb{R}^{d\times\mathcal{S}}$
%	\Loop
%		\State Set $k$ = $k$ + 1
%		\State Draw $n_k =  \beta n_{k-1}$  new random samples 
%		$\{\bm{\xi}_j\}_{j=1}^{n_k}$  $\beta =??$  $j = n_{k-1}+1,\ldots,n_{k-1}+n_k$. 
%        \State $N_\text{total}$ = $N_\text{total}$ + $n_k$    
%	\iffalse	\State Project $\bm{\xi}_k$~$\rightarrow$~$\bm{\theta}_k$. \fi
%		 
%		\State Compute $f(\bm\xi_j)$, $j=n_{k-1}+1, \ldots, n_{k-1}+n_k$.  
%		\State Construct the matrix, $\mat{C}$ and its eigenvalue decomposition
%		\State Compute $\delta W_{1,j}^{(k)}$ = 
%                       \scalebox{1.25}{$\frac{\|(W_{1,j}^{k})^2 - 
%                       (W_{1,j}^{k-1})^2\|}{\|(W_{1,j}^{k-1})^2\|}$}, 
%                       $j = 1,\ldots,\mathcal{S}$.
%		\If {$\max\left(\delta W_{1,j}^{(k)}\right)<\tau$}
%			\State break
%		\EndIf
%	\EndLoop
%	\State Compute $\alpha_i(N_\text{total}) = \sum\limits_{j=1}^{\mathcal{S}} \Lambda_{1_{i,j}}W_{1_{i,j}}^2$,
%	$i=1,\ldots,d$.
%    \EndProcedure
%  \end{algorithmic}
%  \label{alg:free1}
%\end{breakablealgorithm}
%\bigskip
%
\bigskip
\begin{breakablealgorithm}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
  \caption{Algorithm for constructing the matrix, $\mat{C}$}
  \begin{algorithmic}[1]
	\Procedure{Local Linear Approximation}{} 
	\State Draw $N$ random samples, $\{\bm{\xi}_j\}_{j=1}^{N}$ 
	according to $\pi_{\bm{\xi}}$.
	\iffalse \State Project to the physical space:
	$\{\bm{\theta}_k\}_{k=1}^{N}=\theta_l+0.5(\theta_u-\theta_l)\{\bm{\xi}_k\}_{k=1}^{N}$ \fi
	\State Compute $f(\bm\xi_j)$, $j=1, \ldots, N$.
	\State Draw $M$ random samples, $\{\bm{\zeta}_i\}_{i=1}^{M}$
	according to $\pi_{\bm{\xi}}$.
	\State Choose an integer $p \leq N$ 
	\State For each $i=1, \ldots, M$, compute 
	\[
	\begin{aligned}
	\Phi_i &= \{ p \text{ nearest points in } \{\bm{\xi}_j\}_{j=1}^{N} \text{ to } \bm{\zeta}_i\}\\
	\vspace{-2mm}
	\Psi_i &= \text{subset of } f(\bm\xi_j) \text{ corresponding to the points in } \Phi_i
	\end{aligned}
	\]
	\State Compute linear least square fits 
	 $f(\bm\xi_j) \approx c_i + b_i^T\bm{\xi}_j$, \  $\bm{\xi}_j \in \Phi_i, \ f(\bm\xi_j) \in \Psi_i$
	\State Compute the matrix 
	\[
	\hat{\mat{C}} \approx \frac{1}{M} \sum_{i=1}^{M} b_i b_i^T = \hat{\mat{W}}\hat{\mat{\Lambda}}\hat{\mat{W}}^\top
	\]
	\EndProcedure
  \end{algorithmic}
  \label{alg:free2}
\end{breakablealgorithm}
\bigskip

@@

As mentioned earlier, the model output $f(\bm{\xi})$ predominantly varies in the active subspace. Hence, 
$f(\bm{\xi})$ can be transformed as a function of the active variable as $G(\hat{\mat{W}}_1^\top\bm{\xi})$ in
the subspace. The plot of $G$ versus $\hat{\mat{W}}_1^\top\bm{\xi}$, regarded as the \textit{sufficient summary plot} (SSP) is 
compared for the two approaches in Figure~\ref{fig:comp_ssp}.
%
\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.48\textwidth]{./Figures/comp_ssp}
\caption{An illustrative comparison of the SSPs generated using the gradient-based and the gradient-free approaches.}
\label{fig:comp_ssp}
\end{center}
\end{figure}
%
The two SSPs are observed to be in excellent agreement with each other. Moreover, it is interesting to note
that the variability in ignition
delay based on the considered prior marginals for $A_i$'s is observed to be approximately linear in the
active subspace; consistent with the fact the it is 1-dimensional.

We extend the comparative assessment of the two approaches by estimating the activity score for individual
uncertain parameters ($\alpha_i$) using
the components of the dominant eigenvector as shown in Algorithm~\ref{alg:grad}. The activity scores for the 19 
uncertain pre-exponents ($A_i$'s), estimated using
the two approaches are plotted in Figure~\ref{fig:comp_as} (left). Additionally, for the purpose of verification, we 
compare these estimates with those obtained using the DGSMs~\cite{Vohra:2018} in 
Figure~\ref{fig:comp_as} (right). 
%
\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.45\textwidth]{./Figures/comp_as}
  \includegraphics[width=0.45\textwidth]{./Figures/ub_conv_kinetics_rich}
\caption{Left: A bar-graph of activity scores ($\alpha_i$'s) for the 19 uncertain pre-exponents ($A_i$'s).
Right: A plot of the screening metric ($\widehat{\mathcal{C}_i\mu_i}$), defined as a normalized product of the
Poincare constant and the DGSM ($\mu_i$) (adapted from~\cite{Vohra:2018}).}
\label{fig:comp_as}
\end{center}
\end{figure}
%
The activity scores estimated using the two approaches agree favourably with each other as well as those
based on the screening metric involving the DGSMs from~\cite{Vohra:2018}. It is observed that the uncertainty
associated with the ignition delay is largely due to the uncertainty in $A_9$ and $A_1$. Sensitivity towards
$A_{15}$ and $A_{17}$ is also found to be significant.
